3D Magnetic modelling of ellipsoidal bodies

### 2017-01-23 manuscript/manuscript.tex
appendix B

\subsection{Magnetic field produced by ellipsoids}

@@

Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar function
obtained by transforming $f(\mathbf{r})$ (equation \ref{eq:f})
from the main coordinate system to a local coordinate system.
Apparently, the function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
presented by Dirichlet in 1839 as a result of his study about
the gravitational potential produced by homogeneous ellipsoids.
Posteriorly, several authors also deduced and used this function
for describing the magnetic and gravitational fields produced
by ellipsoids \citep{maxwell1873, thomson1879, dubois1896, 
peirce1902, webster1904, kellogg1929, stoner1945, osborn1945, sttraton2007}.

INTRODUZIR A FUNCAO $\tilde{f}(\tilde{\mathbf{r}})$ E ADAPTAR 
O TEXTO ABAIXO

@@

\subsubsection{Internal magnetic field and magnetization}

@@

%\subsection{}                               %% Appendix A1, A2, etc.

>>>>

\subsection{Theoretical background}

@@

\subsection{Coordinate transformation}

Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar function
obtained by transforming $f(\mathbf{r})$ (equation \ref{eq:f})
from the main coordinate system to a local coordinate system.
The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
presented by \citet{dirichlet1839} to describe the gravitational potential
produced by homogeneous ellipsoids.
Posteriorly, several authors also deduced and used this function
for describing the magnetic and gravitational fields produced
by triaxial, prolate, and/or oblate ellipsoids  
\citep{maxwell1873, thomson1879, dubois1896, 
peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
lowes1974,  peake1953, chang1961, clark1986, tejedor1995, sttraton2007}.
It is convenient to use $\tilde{f}_{i}(\tilde{\mathbf{r}})$
and $\tilde{f}_{e}(\tilde{\mathbf{r}})$ to define 
the function $\tilde{f}(\tilde{\mathbf{r}})$ evaluated, 
respectively, at points 
$\tilde{\mathbf{r}}$ inside and outside the volume $V$ of the
ellipsoidal body.

By following \citet{webster1904}, $\tilde{f}_{i}(\tilde{\mathbf{r}})$
is given by
\begin{equation}
\tilde{f}_{i}(\tilde{\mathbf{r}}) = \pi \, abc \, 
\int_{0}^{\infty} \left( 1 
- \frac{\tilde{x}^{2}}{a^{2} + u} 
- \frac{\tilde{y}^{2}}{b^{2} + u}
- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \in V \: ,
\label{eq:fi-tilde}
\end{equation}
where
\begin{equation}
R(u) = \sqrt{\left( a^{2} + u \right)\left( b^{2} + u \right)\left( c^{2} + u \right)} \: .
\label{eq:R}
\end{equation}
This function represents the gravitational potential
that would be produced by the ellipsoidal body at
points located within its volume $V$ if it
had a uniform density equal to the inverse of the
gravitational constant.
Notice that, in this case, the gravitational potential
is a quadratic function of the spatial coordinates
$\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, which
supported the \citeauthor{maxwell1873}'s (\citeyear{maxwell1873})
postulate about uniformly magnetized ellipsoids.

In a similar way, the function $\tilde{f}_{e}(\tilde{\mathbf{r}})$
is given by \citep{webster1904}
\begin{equation}
\tilde{f}_{e}(\tilde{\mathbf{r}}) = \pi \, abc \, 
\int_{\lambda}^{\infty} \left( 1 
- \frac{\tilde{x}^{2}}{a^{2} + u} 
- \frac{\tilde{y}^{2}}{b^{2} + u}
- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \not\in V \: ,
\label{eq:fe-tilde}
\end{equation}
where $R(u)$ is defined by equation \ref{eq:R} and the
parameter $\lambda$ is a constant defining the integral 
lower limit.

The parameter $\lambda$ is defined according to the
ellipsoid type. Details about the mathematical meaning
of this parameter are given in Appendix B.

PAREI AQUI

@@

\subsubsection{Internal magnetic field and demagnetization}

@@

\section{Parameter $\lambda$ and its spatial derivatives}    %% Appendix B

Here, we follow the reasoning presented by \citet{webster1904}
for analysing the parameter $\lambda$ describing triaxial, prolate
and oblate ellipsoids.

\subsection{Parameter $\lambda$ defining triaxial ellipsoids} %% Appendix A1, A2, etc.

Let us consider an ellipsoid with semi-axes $a$, $b$, $c$ oriented along 
the $\tilde{x}$-, $\tilde{y}$-, and $\tilde{z}$-axis, respectively, 
of its local coordinate system, where $a > b > c > 0$. 
This ellipsoid is defined by the following equation:
\begin{equation}
\frac{\tilde{x}^{2}}{a^{2}} + \frac{\tilde{y}^{2}}{b^{2}} + \frac{\tilde{z}^{2}}{c^{2}} = 1 \: .
\label{eq:reference-triaxial-ell}
\end{equation}
A quadric surface which is confocal with the ellipsoid defined in 
equation \ref{eq:reference-triaxial-ell} can be described as 
follows:
\begin{equation}
\frac{\tilde{x}^{2}}{a^{2} + u} + \frac{\tilde{y}^{2}}{b^{2} + u} + \frac{\tilde{z}^{2}}{c^{2} + u} = 1 \: ,
\label{eq:quadric-confocal-triaxial-ell}
\end{equation}
where $u$ is a real number. We know that \ref{eq:quadric-confocal-triaxial-ell} 
represents an ellipsoid for $u$ satisfying the condition
\begin{equation}
u + c^{2} > 0 \: .
\label{eq:condition-triaxial-ell}
\end{equation}

Given $a$, $b$, $c$, and a $u$ satisfying \ref{eq:condition-triaxial-ell}, 
we may use \ref{eq:quadric-confocal-triaxial-ell} for determining a set of 
points $(x, y, z)$ lying on the surface of an ellipsoid which is confocal 
with that one defined in equation \ref{eq:reference-triaxial-ell}. 
Now, consider the problem of determining the ellipsoid which is confocal 
with that one defined in \ref{eq:reference-triaxial-ell} and pass through 
a particular point $(\tilde{x}, \tilde{y}, \tilde{z})$. 
This problem consists in determining the real number $u$ that, 
given $a$, $b$, $c$, $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, 
satisfies the condition expressed by equation \ref{eq:condition-triaxial-ell}.
By rearranging equation \ref{eq:quadric-confocal-triaxial-ell}, 
we obtain the following cubic equation for $u$:
\begin{equation}
p(u) = (a^{2} + u)(b^{2} + u)(c^{2} + u) - (b^{2} + u)(c^{2} + u) \, \tilde{x}^{2}
- (a^{2} + u)(c^{2} + u) \, \tilde{y}^{2} - (a^{2} + u)(b^{2} + u) \, \tilde{z}^{2} \: .
\label{eq:cubic-equation-triaxial-ell}
\end{equation}
By analysing the signals of this cubic equation we conclude that:
\begin{equation}
u = \begin{cases}
d \to \infty \: &, \quad p(u) > 0 \\
-c^{2} \: &, \quad p(u) < 0 \\
-b^{2} \: &, \quad p(u) > 0 \\
-a^{2} \: &, \quad p(u) < 0
\end{cases} \: .
\label{eq:cubic-equation-signals-triaxial-ell}
\end{equation}
Notice that, according to \ref{eq:cubic-equation-signals-triaxial-ell},
the smaller, intermediate and largest roots of the cubic 
equation $p(u)$ (equation \ref{eq:cubic-equation-triaxial-ell}) are 
located, respectively, in the intervals $[ -a^{2} \, , -b^{2} ]$,
$[ -b^{2} \, , -c^{2} ]$ and $[ -c^{2} \, , \infty [$.
Remember that we are interested in a $u$ satisfying 
the condition expressed by equation \ref{eq:condition-triaxial-ell}. 
Consequently, according to the signal analysis shown in equation
\ref{eq:cubic-equation-signals-triaxial-ell}, we are interested in 
the largest root $\lambda$ of the cubic equation $p(u)$ (equation
\ref{eq:cubic-equation-triaxial-ell}).

From equation \ref{eq:cubic-equation-triaxial-ell}, we obtain a
simpler one given by
\begin{equation}
p(u) =  u^{u} + p_{2} \, u^{2} + p_{1} \, u + p_{0} \: ,
\label{eq:cubic-equation-triaxial-ell-simpler}
\end{equation}
where
\begin{equation}
p_{2} = a^{2} + b^{2} + c^{2} - \tilde{x}^{2} - \tilde{y}^{2} - \tilde{z}^{2} \: ,
\label{eq:p2-triaxial-ell}
\end{equation}
\begin{equation}
p_{1} = p_{1} =  ^{2} \, c^{2} + a^{2} \, c^{2} + a^{2} \, b^{2} 
- (b^{2} + c^{2}) \, \tilde{x}^{2}
- (a^{2} + c^{2}) \, \tilde{y}^{2} 
- (a^{2} + b^{2}) \, \tilde{z}^{2}
\label{eq:p1-triaxial-ell}
\end{equation}
and
\begin{equation}
p_{0} =  a^{2} \, b^{2} \, c^{2} - b^{2} \, c^{2} \, 
\tilde{x}^{2} - a^{2} \, c^{2} \, \tilde{y}^{2} - a^{2} \, 
b^{2} \, \tilde{z}^{2} \: .
\label{eq:p0-triaxial-ell}
\end{equation}
Finally, from equations \ref{eq:p2-triaxial-ell}, 
\ref{eq:p1-triaxial-ell} and \ref{eq:p0-triaxial-ell},
the largest root $\lambda$ of $p(u)$ 
(equation \ref{eq:cubic-equation-triaxial-ell}) can be 
calculated as follows \citep{weisstein2017}:
\begin{equation}
\lambda = 2 \, \sqrt{-Q} \, \cos \left( \frac{\theta}{3}\right) - \frac{p_{2}}{3} \: ,
\label{eq:lambda-triaxial-ell}
\end{equation}
where
\begin{equation}
\theta = \cos^{-1} \left( \frac{R}{\sqrt{Q^{3}}} \right) \: ,
\label{eq:theta-triaxial-ell}
\end{equation}
\begin{equation}
Q = \frac{3 \, p_{1} - p_{2}^{2}}{9}
\label{eq:Q-triaxial-ell}
\end{equation}
and
\begin{equation}
R = \frac{9 \, p_{1} \, p_{2} - 27 \, p_{0} - 2 \, p_{2}^{3}}{54} \: .
\label{eq:R-triaxial-ell}
\end{equation}

\subsection{Parameter $\lambda$ defining prolate and oblate ellipsoids} %% Appendix A1, A2, etc.

Let us now consider a prolate ellipsoid with semi-axes $a$, $b$, 
$c$ oriented along the $\tilde{x}$-, $\tilde{y}$-, and 
$\tilde{z}$-axis, respectively, of its local coordinate system, 
where $a > b = c > 0$.

In this case,
